Four reasons your build is slow

### 2019-01-17 paper.tex
3.4

Google's protocol buffers project \cite{protobufs3.6.1} exhibited this behavior.  It's work was calculated
to be about 16.7 minutes and it had a relatively
long predicted span of 43.7 seconds, which was dominated by a call to g++ compiling
a single file.  When the analysis applied in section \ref{sec:expensive} is applied
to protocol buffers' build, we learn that the top three spans are dominated by the
single file compilations of the files in fig. \ref{code:g++1}.  If the g++ compilations
of these three files were not in the build's span the new span would be about 20s,
roughly half of the original span.  Speeding up the compilation of these three files
would be a good place to begin improving the parallelism of this build.

\begin{figure}[H]
\begin{Verbatim}[commandchars=\\\{\},codes={\catcode`$=3\catcode`^=7\catcode`_=8},fontsize=\small]
  google/protobuf/descriptor.cc
  google/protobuf/descriptor.pb.cc
  google/protobuf/compiler/cpp/cpp\_message.cc
\end{Verbatim}
\caption{The compilation of these 3 files dominate the longest 3 spans.}
\label{code:g++1}
\end{figure}

>>>>

Google's protocol buffers project \cite{protobufs3.6.1} exhibited this
behavior.  It's work was calculated to be about 16.7 minutes and it
had a relatively long predicted span of 43.7 seconds, which was
dominated by a call to g++ compiling a single file.  When the analysis
applied in section \ref{sec:expensive} is applied to protocol buffers'
build, we learn that the top three spans are dominated by the single
file compilations of the files in fig. \ref{code:g++1}.  If the g++
compilations of these three files were not in the build's span the new
span would be about 20s, roughly half of the original span.  Speeding
up the compilation of these three files would be a good place to begin
improving the parallelism of this build, perhaps by breaking
individual files into multiple files. Our tool is automatically able
to pinpoint where this would be profitable, and to show that further
efforts past these three would have diminishing returns.

\begin{figure}[t]
\begin{Verbatim}[fontsize=\small]
[span: 42.7; 38.7]
 Longest part of span is `g++ descriptor.cc`
Without this: [span: 30.45; 26.36]
 Longest part of span is `g++ descriptor.pb.cc`
Without this: [span: 28.73; 26.35]
 Longest part of span is `g++ cpp_message.cc`
Without this: [span: 19.78; 17.4]
\end{Verbatim}
\caption{Output of our tool describing the protobuf build (simplified)}
\label{code:g++1}
\end{figure}
